Simulations of Ballot Polling Risk-Limiting Audits

### 2021-11-02 MultipleRoundSims/sections/01-intro.tex
intro

\subsection{Our Results}
We show the following: 
\begin{enumerate}
\item Even when the first round stopping probability is as small as $0.25$, the number of ballots required for \Minerva is smaller than that required by SO \BRAVO and EoR \BRAVO. However, the improvement is considerably smaller than that when the stopping probability is $0.9$. 
\begin{itemize}
\item The number of ballots required by SO \BRAVO for a first round stopping probability of $0.9$ is about a third more than that required by \Minerva. On the other hand, for a first round stoping probability of $0.25$, it requires only about a fourth to a half more ballots (depending on margin) than does \Minerva.  
\item The number of ballots required by EoR \BRAVO for a first round stopping probability of $0.9$ is about twice those required by \Minerva. On the other hand, for a first round stoping probability of $0.25$, it requires only about a tenth more ballots than does \Minerva.  
\end{itemize}
\item For a first round stopping probability of $0.9$, when consequent \Minerva rounds are the same size (multiplying factor $1$), consequent conditional stopping probabilities are about $0.75$ and $0.74$ respectively for rounds two and three. When the multiplying factor is $1.5$, the conditional stopping probabilities for rounds two and three are $0.91$ and $0.83$ respectively. 
\item Our simulations may be used to study the stopping probabilities and maximum risks of the different audits for different stopping probabilities for the first round, we provide examples. 
\end{enumerate}

>>>>

\subsection{Our Contributions}
We show the following: 
\begin{enumerate}
\item Even when the first round stopping probability is as small as $0.25$, the number of ballots required for \Minerva is smaller than that required by SO \BRAVO and EoR \BRAVO. However, the improvement is considerably smaller than that when the stopping probability is $0.9$. 
\begin{itemize}
\item The number of ballots required by SO \BRAVO for a first round stopping probability of $0.9$ is about a third more than that required by \Minerva. On the other hand, for a first round stopping probability of $0.25$, it requires only about a tenth more ballots than does \Minerva.  
\item The number of ballots required by EoR \BRAVO for a first round stopping probability of $0.9$ is about twice those required by \Minerva. On the other hand, for a first round stopping probability of $0.25$, it requires only about a fourth to a half more ballots (depending on margin) than does \Minerva.  
\end{itemize}
\item For a first round stopping probability of $0.9$, when consequent \Minerva rounds are the same size (multiplying factor $1$), consequent conditional stopping probabilities are about $0.75$ and $0.74$ respectively for rounds two and three. When the multiplying factor is $1.5$, the conditional stopping probabilities for rounds two and three are $0.91$ and $0.83$ respectively. 
\item Our simulations may be used to study the stopping probabilities and maximum risks of the different audits for different stopping probabilities for the first round, we provide examples. 
\end{enumerate}
